### 2015-12-03 paper.tex
Reformat figure syntax and use file extensions
More figure and equation syntax cleanup
Add uncertainty analysis section from test plan report

\begin{figure}[h]
\includegraphics[width=0.65\textwidth]{figures/turbine}
\caption{{\bf Turbine Model.}
A drawing of the turbine model.}
\label{fig:turbine-drawing}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/turbine_coordinate_system}
\caption{{\bf Coordinate system.} Wake measurement coordinate system and
cross-stream/vertical coordinates. All dimensions are in meters.}
\label{fig:coordinates}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/cp_curves}
\caption{{\bf Power Coefficient Curves.}
Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{fig:cp-curves}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/cd_curves}
\caption{{\bf Drag Coefficient Curves.}
Mean rotor drag coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{fig:cd-curves}
\end{figure}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/perf_re_dep}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/meancontquiv}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/k_contours}

@@

\begin{figure}[ht!]
\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}

@@

\begin{figure}[ht!]
\includegraphics[width=\textwidth]{figures/no_blades_all}
\caption{{\bf Strut drag losses.}
Measurements of the strut drag losses for (a) NACA 0021 and (b) cylindrical
struts, both stationary and towed.}
\label{fig:no-blades}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\textwidth]{figures/perf_covers}
\caption{{\bf High drag strut performance.}
Turbine performance and rotor drag coefficient curves with both NACA 0021
and cylindrical struts.}
\label{fig:perf-covers}
\end{figure}

>>>>

\begin{figure}[h]
    \includegraphics[width=0.65\textwidth]{figures/turbine.eps}

    \caption{{\bf Turbine Model.} A drawing of the turbine model.}

    \label{fig:turbine-drawing}
\end{figure}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}

    \caption{{\bf Coordinate system.} Wake measurement coordinate system and
    cross-stream/vertical coordinates. All dimensions are in meters.}

    \label{fig:coordinates}
\end{figure}

\subsection*{Uncertainty Analysis}

Uncertainty was considered from a combination of systematic
and random errors. The random error was inferred from the sample standard
deviation and the systematic from the sensor calibrations or datasheets.
Combining both sources of error, along with their propagation into quantities
derived from multiple measurements, followed the procedures outlined in
Coleman and Steele (2009) \cite{ColemanSteele}, described below.

An expanded uncertainty interval with 95\% confidence was computed for
$\lambda$, $C_P$, and $C_D$
\begin{equation}
    U_{95} = t_{95} u_c,
\end{equation}
where $t_{95}$ is the value from the Student-$t$ distribution for a 95\%
confidence interval and $u_c$ is the combined standard uncertainty. Combined
standard uncertainty for a given quantity $X$ is calculated by
\begin{equation}
    u_X^2 = s_X^2 + b_X^2,
\end{equation}
where $s_X$ is the sample standard deviation, calculated as the standard
deviation of the mean per turbine revolution, and $b_X$ is the systematic
uncertainty, computed by
\begin{equation}
    b_{X}^2 = \sum_{i=1}^J \left( \frac{\partial X}{\partial x_i} \right)^2
    b_{x_i}^2,
\end{equation}
where $x_i$ is a primitive quantity used to calculate $X$ (e.g. $T$, $\omega$,
and $U_\infty$ for calculating $C_P$), and $b_{x_i}$ is the primitive quantity's
systematic uncertainty, estimated as half the value listed in
Table~\ref{tab-sensors}.

Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which can
be obtained using the Welch--Satterthwaite formula
\begin{equation}
    \nu_X = \frac{\left(s_X^2 + \sum_{k=1}^M b_k^2 \right)^2} {s_X^4/\nu_{s_X} +
        \sum_{k=1}^M b_k^4/\nu_{b_k}},
\end{equation}
where $\nu_{s_X}$ is the number of degrees of freedom associated with $s_X$ and
$\nu_{b_k}$ is the number of degrees of freedom associated with $b_k$.
$\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
samples (or turbine revolutions). $\nu_{b_k}$ will be estimated as
\begin{equation}
    \nu_{b_k} = \frac{1}{2} \left( \frac{\Delta b_k}{b_k} \right)^{-2},
\end{equation}
where the quantity in parentheses is the relative uncertainty of $b_k$.

From previous measurements of a similarly-sized vertical-axis turbine with the
same experimental setup, we expect expanded uncertainties for $\lambda$, $C_P$,
and $C_D$ to be approximately 0.008, 0.01, and 0.02, respectively, at a tow
speed $U_\infty = 1.0$ m/s. These values are well within the discrepancies
between previous measurements and predictions by CACTUS \cite{Michelen2014},
making the data from the experiments described here suitable for model validation.

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/cp_curves.eps}

    \caption{{\bf Power Coefficient Curves.} Mean rotor power coefficient
    plotted versus mean tip speed ratio for multiple Reynolds numbers.}

    \label{fig:cp-curves}
\end{figure}

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/cd_curves.eps}

    \caption{{\bf Drag Coefficient Curves.} Mean rotor drag coefficient plotted
    versus mean tip speed ratio for multiple Reynolds numbers.}

    \label{fig:cd-curves}
\end{figure}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/meancontquiv.eps}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/k_contours.eps}

@@

\begin{figure}[ht!]
    \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}

@@

\begin{figure}[ht!]
    \includegraphics[width=\textwidth]{figures/no_blades_all.eps}

    \caption{{\bf Strut drag losses.} Measurements of the strut drag losses for
    (a) NACA 0021 and (b) cylindrical struts, both stationary and towed.}

    \label{fig:no-blades}
\end{figure}

\begin{figure}[ht!]
    \includegraphics[width=\textwidth]{figures/perf_covers.eps}

    \caption{{\bf High drag strut performance.} Turbine performance and rotor
    drag coefficient curves with both NACA 0021 and cylindrical struts.}

    \label{fig:perf-covers}
\end{figure}
